---
title: "A week in MDS"
author: "Rachel K. Riggs"
date: "September 22, 2018"
output:
  ioslides_presentation:
    widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Monday through Thursday 

- wake up really early
- go to lectures
- go to labs
- stay on campus to get more work done
- calculate amount of time needed to sleep

```{r sleep time, echo = TRUE}
night_hours <- 24 - 22
morning_hours <- 0 + 5.5
amount_of_sleep <-  night_hours + morning_hours
print(paste0("Try get to at least ", amount_of_sleep, " hours of sleep."))
```

## Friday

- get up early, but not as early as Mon-Thurs
- work on labs all day
- eat dinner
- sleep a bit more than Mon-Thurs

## Saturday

- get up early
- work on labs all day
- **SUBMIT LABS BY 6PM!!!**
- make pizza
- eat pizza and have a beer

## Sunday {.smaller}

- get up early
- work out
- calculate ratio of free time vs time needed to study/read/etc.

```{r time for study vs play, echo = TRUE, tidy=TRUE}
hours_in_day_awake <- 24 - 8
hours_study = 4
hours_free = 5
print(paste("This Sunday I get", (hours_free/hours_in_day_awake)*100, "% free time vs.", (hours_study/hours_in_day_awake)*100,"% work time. The rest is for sleep, cleaning, and errands."))

```



